### 2019-09-15 ic-journal/conclusions.tex
Updated generated TeX files

The formalisation has actually focused on the theory of
unique solution of equations and contractions. It    
 has also allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity. 
The formalisation brings up and exploits similarities between results
and proofs for different equivalences and preorders. Indeed we have
considered several `unique-solution' results (for various equivalences
and preorders); they share many parts of the proofs, but present a few
delicate and subtle differences in a few points. In a paper-pencil
proof, checking all details would be long and \hl{error-prone},
\hl{especially in cases where the proofs are similar to each other or
  when there are long case analyses to be carried out.}
A theorem-prover formalisation is in this respect  helpful and reassuring.
We think that the statements in the formalisation are easy to read and
understand, as they are  close to the original statements found in
standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.

>>>>

The formalisation has actually focused on the theory of
unique solution of equations and contractions. It    
 has also allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity. 
The formalisation brings up and exploits similarities between results
and proofs for different equivalences and preorders. Indeed we have
considered several `unique-solution' results (for various equivalences
and preorders); they share many parts of the proofs, but present a few
delicate and subtle differences in a few points. In a paper-pencil
proof, checking all details would be long and \hl{error-prone},
\hl{especially in cases where the proofs are similar to each other or
  when there are long case analyses to be carried out.}
Some of the textbook proofs are even wrong, e.g. Milner's
proof of the unique-solution theorem for $wb$
(Theorem~\ref{t:Mil89s3}).
For some other textbook proofs, even they are correct, sometimes they actually
do not need all information from the antecedents, which can be further
weakened. This kind of improvements can be easily found during the
formalisation work.
For our CCS formalisation, we believe that all the definitions and
theorem statements are easy to read and
understand, as they are very close to their original statements in
textbooks~\cite{Gorrieri:2015jt,Mil89}.
